Response to the defense feedback

### 2021-06-19 Chapter-3/Chapter-3.tex
Updates from Overleaf

For one execution, a program ($\beta$) has many temporary values ($t_i \in
  T$). Once $\beta$ (program), $k$ (secret), and $m$ (message, public) are
determined, $t_i$ is also fixed. Therefore, $ t_i = f_i(\beta, k, m)$, where $f_
  i$ is a function that maps between $t_i$ and ($\beta$, $k$, $m$). In the chapter,
we consider two code patterns that can be exploited by an attacker,
\emph{secret-dependent control transfers} and \emph{secret-dependent data
  accesses}.

\subsection{Secret-dependent Control Transfers}
A control-flow path is secret-dependent if different input-sensitive keys
($K$) can lead to different branch conditions.
We define a branch to be secret-dependent if
$$\exists k_{i1}, k_{i2} \in K, m \in M, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m) \land PC,$$

\noindent where $PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers. Note that in the
above definition, $m$ is also a variable. So it is possible for some $m \in M$,
we cannot find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above inequation. For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2. However, if $m = \mathtt{0xffffffff}$ and $k = \mathtt{0}$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.

>>>>

For one execution, a program ($\beta$) has many temporary values ($t_i \in
  T$). Once $\beta$ (program), $k$ (secret), and $m$ (message, public) are
determined, $t_i$ is also fixed. Therefore, $ t_i = f_i(\beta, k, m)$, where $f_
  i$ is a function that maps between $t_i$ and ($\beta$, $k$, $m$). In this dissertation,
we consider two code patterns that can be exploited by an attacker,
\emph{secret-dependent control transfers} and \emph{secret-dependent data
  accesses}.

\subsection{Secret-dependent Control Transfers}
A control-flow path is secret-dependent if there are two different input-sensitive keys
($K$) that can lead to different branch conditions.
We define a branch to be secret-dependent if
$$\exists k_{i1}, k_{i2} \in K, m \in M, \,f_i(\beta, k_{i1}, m) \neq f_i(\beta, k_{i2}, m) \land PC,$$

\noindent where $PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers. Note that in the
above definition, $m$ is also a variable. So it is possible for some $m \in M$,
we cannot find a pair of two different $k_{i1}$ and $k_{i2}$ satisfying the above inequation. For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2. However, if $m = \mathtt{0xffffffff}$ and $k = \mathtt{0}$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.
